\bf Comparing the Power of Plot Designs to Reveal Correlation

### 2015-12-10 paper/paper.Rnw
Updates

\begin{figure}[htbp]
  \centering
  \includegraphics{cny line}
  \caption{Exchange rates for Australian dollars and Chinese yuan against the United States dollar from Mar 30-May 2, 2015, shown as overlaid time series. (Both sets of values were standardized to bring them to the same scale for plotting.) What would you report the correlation between the two series to be?}
  \label{cny}
\end{figure}

@@

\begin{figure}[htbp]
  \centering
  \begin{subfigure}
    \includegraphics{nzd scatter}
  \end{subfigure}
  \begin{subfigure}
    \includegraphics{nzd line}
  \end{subfigure}
  \caption{ Exchange rates for Australian and NZ dollars against US dollar, from Mar 30-May 2, 2015, shown using a scatterplot (left) and overlaid line graph (right). Which one can you read the correlation from more accurately? Point-wise correlation between the two series, ignoring autodependence, is 0.64.}
  \label{nzd}
\end{figure}

@@

\begin{figure}[htbp]
  \centering
<<pins, dependson='samplesize', fig.width=6, fig.height=10, out.width='0.7\\textwidth', echo=FALSE>>=
# correl <- read.csv("correlations.csv") # You have already read this
pin <- select(full, pic_id, response_0, actual_location, 
              test_param, smoothed, n) #full[,c(5, 6, 10, 15, 16, 17)]
# Need to use the tidyr commands instead of cSplit
# Here's where we will need to make some changes to incorporate the multiple picks
pin <- pin %>% transform(response_0= strsplit(as.character(response_0), ",")) %>% unnest(response_0)
pin$response_0 <- as.integer(pin$response_0)
counts <- data.frame(table(pin$pic_id, pin$response_0))
counts$Var1 <- as.integer(counts$Var1)
counts$Var2 <- as.integer(counts$Var2)
colnames(counts) <- c("lineup", "plot", "count")
pin <- merge(counts, Turk, by.x="lineup", by.y="pic_id")
pin <- select(pin, lineup, plot, count, smoothed, true_pos, n, test_param, r)#pin[,c(1, 2, 3, 12, 13, 15, 11, 20)]
pin$r <- factor(pin$r)
#colnames(pin) <- c("lineup", "plot", "count", "smoothed", "true_pos", "n", "design", "r")
pin <- mutate(pin, design=ifelse(test_param=="scatter", "Scatterplot", "Overlaid Lines"))#, smoothed=ifelse(smoothed=="no", 0, 1))
pin$base <- 0
pin$Correlation <- diag(as.matrix(correl[pin$lineup, (pin$plot+2)]))
pin <- mutate(pin, true = ifelse(plot==true_pos, "True plot", "Null plot"))
pin <- merge(pin, Turk[,c(2, 16)], by.x = "lineup", by.y = "pic_id")
pin <- mutate(pin, percent = count/attempt)
ggplot(data=subset(pin, smoothed=="no" & design == "Scatterplot")) + geom_errorbar(aes(x=Correlation, ymin=base, ymax=percent, colour=true)) +
       geom_point(aes(x=Correlation, y=percent, colour=true)) + coord_fixed() + facet_grid(n~r) + labs(title="Unsmoothed Scatterplot", y="Percent Chosen") + theme(legend.position="none")
ggplot(data=subset(pin, smoothed=="yes" & design == "Scatterplot")) + geom_errorbar(aes(x=Correlation, ymin=base, ymax=percent, colour=true)) +
  geom_point(aes(x=Correlation, y=percent, colour=true)) + coord_fixed()  + facet_grid(n~r) + labs(title="Smoothed Scatterplot", y="Percent Chosen") + theme(legend.position="none")
ggplot(data=subset(pin, smoothed=="no" & design == "Overlaid Lines")) + geom_errorbar(aes(x=Correlation, ymin=base, ymax=percent, colour=true)) +
  geom_point(aes(x=Correlation, y=percent, colour=true)) + coord_fixed()  + facet_grid(n~r) + labs(title="Unsmoothed Overlaid Lines", y="Percent Chosen") + theme(legend.position="none")
ggplot(data=subset(pin, smoothed=="yes" & design == "Overlaid Lines")) + geom_errorbar(aes(x=Correlation, ymin=base, ymax=percent, colour=true)) +
  geom_point(aes(x=Correlation, y=percent, colour=true)) + coord_fixed()  + facet_grid(n~r) + labs(title="Smoothed Overlaid Lines", y="Percent Chosen") + theme(legend.position="none")

#Code to be fixed
@
  \label{pins}
  \caption{Pin plots of the subject selections of each lineup. On the x-axis is the correlation of the plot (there is potentially spurious correlation in the null plots), and on the y-axis is the proportion a plot was chosen. Red pins indicate null plots and blue indicates the true plot, occasionally the true plot does not appear as it has a frequency of zero and is visually blocked by the red pins. The pin plots are split with true plot correlation on the columns and sample size on the rows. Each plot contains information from all three lineups with that unique combination of factors: plot design, smoothness, sample size and true correlation.}
\end{figure}

@@

# Need to keep only evaluations done by subject who completed at least 10
x <- data.frame(table(full$subj_id))
keep <- x$Var1[x$Freq>9]
full.sub <- filter(full, subj_id %in% keep)
full.sub$r <- round(full.sub$correlation, 1)
full.sub$rsgn <- ifelse(full.sub$r >= 0, 1, 0)
full.sub$rabs <- abs(full.sub$r)
full.sub$rabs <- factor(full.sub$rabs)
full.sub$plot <- ifelse(full.sub$test_param == 0, "S", "L")
full.sub <- full.sub[,c(1,7, 15,16,17,20:26)]
full.sub$rpos <- ifelse(full.sub$r > 0, full.sub$r, 0)
full.sub$rneg <- ifelse(full.sub$r < 0, full.sub$r, 0)
full.sub$alpha <- log(.05/0.95)

@@

<<timefit, dependson='powerfit', echo=FALSE, results=hide, message=FALSE, error=FALSE, warning=FALSE>>=
timelmer <-  lmer(log_time ~ smoothed + r + n + rsgn*r + test_param + test_param*smoothed 
                  + test_param*r + test_param*n + test_param*rsgn*r + test_param*correct + (1|subj_id), data=full.sub)
@
%get table code

>>>>

\begin{figure}[htbp]
  \centering
  \includegraphics{cnyline}
  \caption{Exchange rates for Australian dollars and Chinese yuan against the United States dollar from Mar 30-May 2, 2015, shown as overlaid time series. (Both sets of values were standardized to bring them to the same scale for plotting.) What would you report the correlation between the two series to be?}
  \label{cny}
\end{figure}

@@

\begin{figure}[htbp]
  \centering
  \begin{subfigure}
    \includegraphics{nzdscatter}
  \end{subfigure}
  \begin{subfigure}
    \includegraphics{nzdline}
  \end{subfigure}
  \caption{Exchange rates for Australian and NZ dollars against US dollar, from Mar 30-May 2, 2015, shown using a scatterplot (left) and overlaid line graph (right). Which one can you read the correlation from more accurately? Point-wise correlation between the two series, ignoring autodependence, is 0.64.}
  \label{nzd}
\end{figure}

@@

\begin{figure}[htbp]
  \centering
%<<pins, dependson='samplesize', fig.width=6, fig.height=10, out.width='0.7\\textwidth', echo=FALSE>>=
\iffalse
# correl <- read.csv("correlations.csv") # You have already read this
pin <- select(full, pic_id, response_0, actual_location, 
              test_param, smoothed, n) #full[,c(5, 6, 10, 15, 16, 17)]
# Need to use the tidyr commands instead of cSplit
# Here's where we will need to make some changes to incorporate the multiple picks
pin <- pin %>% transform(response_0= strsplit(as.character(response_0), ",")) %>% unnest(response_0)
pin$response_0 <- as.integer(pin$response_0)
counts <- data.frame(table(pin$pic_id, pin$response_0))
counts$Var1 <- as.integer(counts$Var1)
counts$Var2 <- as.integer(counts$Var2)
colnames(counts) <- c("lineup", "plot", "count")
pin <- merge(counts, Turk, by.x="lineup", by.y="pic_id")
pin <- select(pin, lineup, plot, count, smoothed, true_pos, n, test_param, r)#pin[,c(1, 2, 3, 12, 13, 15, 11, 20)]
pin$r <- factor(pin$r)
#colnames(pin) <- c("lineup", "plot", "count", "smoothed", "true_pos", "n", "design", "r")
pin <- mutate(pin, design=ifelse(test_param=="scatter", "Scatterplot", "Overlaid Lines"))#, smoothed=ifelse(smoothed=="no", 0, 1))
pin$base <- 0
pin$Correlation <- diag(as.matrix(correl[pin$lineup, (pin$plot+2)]))
pin <- mutate(pin, true = ifelse(plot==true_pos, "True plot", "Null plot"))
pin <- merge(pin, Turk[,c(2, 16)], by.x = "lineup", by.y = "pic_id")
pin <- mutate(pin, percent = count/attempt)
ggplot(data=subset(pin, smoothed=="no" & design == "Scatterplot")) + geom_errorbar(aes(x=Correlation, ymin=base, ymax=percent, colour=true)) +
       geom_point(aes(x=Correlation, y=percent, colour=true)) + coord_fixed() + facet_grid(n~r) + labs(title="Unsmoothed Scatterplot", y="Percent Chosen") + theme(legend.position="none")
ggplot(data=subset(pin, smoothed=="yes" & design == "Scatterplot")) + geom_errorbar(aes(x=Correlation, ymin=base, ymax=percent, colour=true)) +
  geom_point(aes(x=Correlation, y=percent, colour=true)) + coord_fixed()  + facet_grid(n~r) + labs(title="Smoothed Scatterplot", y="Percent Chosen") + theme(legend.position="none")
ggplot(data=subset(pin, smoothed=="no" & design == "Overlaid Lines")) + geom_errorbar(aes(x=Correlation, ymin=base, ymax=percent, colour=true)) +
  geom_point(aes(x=Correlation, y=percent, colour=true)) + coord_fixed()  + facet_grid(n~r) + labs(title="Unsmoothed Overlaid Lines", y="Percent Chosen") + theme(legend.position="none")
ggplot(data=subset(pin, smoothed=="yes" & design == "Overlaid Lines")) + geom_errorbar(aes(x=Correlation, ymin=base, ymax=percent, colour=true)) +
  geom_point(aes(x=Correlation, y=percent, colour=true)) + coord_fixed()  + facet_grid(n~r) + labs(title="Smoothed Overlaid Lines", y="Percent Chosen") + theme(legend.position="none")

#Code to be fixed
\fi
%@

  \label{pins}
  \caption{Pin plots of the subject selections of each lineup. On the x-axis is the correlation of the plot (there is potentially spurious correlation in the null plots), and on the y-axis is the proportion a plot was chosen. Red pins indicate null plots and blue indicates the true plot, occasionally the true plot does not appear as it has a frequency of zero and is visually blocked by the red pins. The pin plots are split with true plot correlation on the columns and sample size on the rows. Each plot contains information from all three lineups with that unique combination of factors: plot design, smoothness, sample size and true correlation.}
\end{figure}

@@

# Need to keep only evaluations done by subject who completed at least 10
x <- data.frame(table(full$subj_id))
keep <- x$Var1[x$Freq>9]
full.sub <- filter(full, subj_id %in% keep)
full.sub$r <- round(full.sub$correlation, 1)
full.sub$rsgn <- ifelse(full.sub$r >= 0, 1, 0)
full.sub$rabs <- abs(full.sub$r)
full.sub$rabs <- factor(full.sub$rabs)
full.sub$plot <- ifelse(full.sub$test_param == 0, "S", "L")
full.sub <- select(full.sub, correct, r, rsgn, smoothed, n, subj_id, plot, log_time)
full.sub$alpha <- log(.05/0.95)

@@

<<timefit, dependson='powerfit', echo=FALSE, results=hide, message=FALSE, error=FALSE, warning=FALSE>>=
timelmer <-  lmer(log_time ~ plot*smoothed + plot*n + plot*rsgn*r + plot*correct + (1|subj_id), data=full.sub)
@
%get table code
